Refinements for open automata

### 2023-02-21 2021-Refinement/paper/refinementarticleV2.tex
Theorem 3
Congruence in progress

In this case the composition gives: \[g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} \text{ and }
g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}\]
As $k \in H$ we have   
$\beta_{1k} = \beta_{2xk}$ then we  deduce:
\[g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}\]
The proof of the rest  is based on the following facts: 
\begin{enumerate}
\item  Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.   By construction of  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
\alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.
\item By composition we have also: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^1 \land \beta^1_{3j}= \beta^2_{3j})\]
\item 
Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: \\
${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
The disjunction with the following hypothesis:\\ $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$  will give:
\begin{align*}
 V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash &    \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
\Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}
\end{align*}
\end{enumerate}

@@

\RAB{ I think there is no need to the no blocking condition} Furthermore, by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
Thus, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
		  \wedge \cancel{\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\wedge} \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
		\end{array}}   
\end{multline*}

From the two previous formulas, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13} \land \cancel{\reach{A_{13}}\mpar{s_{13}} \land} \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}		\nwedge\\
			  R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
 \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
		\end{array}}   
\end{multline*}

@@

\item \TODO{To check this point:} Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
\begin{multline*}
V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ R\mpar{s_{13}, s_{23}} \nwedge  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg (\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}) 
\end{multline*}

Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
\begin{multline*}
V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies   \neg(\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2})
\end{multline*}
Because the guards from transitions of $A_1$ are still transitions of $A_{13}$, we get:  
\begin{multline*}
V_{13}  \uplus \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}} \vdash \neg(\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
\end{multline*}

Similarly, transitions of $A_2$ are still transitions of $A_{23}$,  we get:
\begin{multline*}
V_{23}  \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash \neg(\bigvee_\subbox{t_1 \in \fOT{s_2}} \fguard{t_2}) \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
\end{multline*}
From the three previous formulas we deduce:
  \begin{multline*}
V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ R\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
\end{multline*}

which also implies:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \underbrace{R\mpar{s_1, s_2} \wedge  \mpar{\,\,\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 \wedge s^1_3=s^2_3}}_{R^{\prime}(s_{13},s_{23})}  \wedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})   \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
\end{multline*}
which gives us what we needed to demonstrate. \qed

@@

\begin{align*}
		&  \OTx{12}{}{12}{12} \in \fOT{s_{12}}
\end{align*}		
there exists an indexed family $t_{13x}$ of OTs originating from $s_{13}$ that simulates it: 
\begin{align*}
		&  \mpar{\OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X}
\end{align*}	
such that  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
\begin{multline*}	
V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}} 
	\end{multline*}
By definition of composition and open automata refinement we have: 
\begin{align*}
&V_{12}= V^1_1\uplus V_3 \text{ and }
V_{13}= V^2_1\uplus V_3\\
& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\} = \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} = J_{12 } \cap J_{13} \\
\end{align*}
We have by hypothesis $\wrel{A_2}{A_3}{H}$, then for any open transition $t_2$ in $T_2$  originating from $s_2$:
\begin{align*}
\OTx{2}{}{2}{2} \in \fOT{s_2}
\end{align*}
there exists an indexed family of OTs originating from $s_{2}$: 
\begin{align*}
\mpar{\OTx{3}{x}{3x}{3x} \in \fOT{s_{3}}}^{x \in X} 
\end{align*}
such that $\forall x \in X, J'_{3x} \cap H = J'_2 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ R\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj} \nwedge\\
			 g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
		\end{array}}  \qquad \quad (*)
\end{multline*}	
\smallskip

@@

\paragraph{First case: Both automata perform a transition.} The transition $t_{12}$  is obtained by the composition of transition $t_2=\OTx{2}{}{2}{2}$ and a transition \[t_1^1=
\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
\] The result:
%%%% Attention deactiver ici
\[
t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}',s'_2 }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2j})^{j \in J^{\prime}_2} }}{g^1_1 \wedge g_2 \wedge \alpha_2 = \beta^1_{1k}}{\psi^1_1 \uplus \psi_2} \qquad \text{ where } k \in {J^1_{1}}^{\prime} 
\]

We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (as stated above).
By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$.
\[
t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{j \in J^{2 \prime}_1}}\uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}} }{g_{3x} \wedge g^2_1 \wedge \alpha^2_1 = \beta_{3xk}}{\psi_{3x} \uplus \psi^2_1}
\right)^{x\in X}\]
Recall that in this case  $k \in {J^1_{1}}^{\prime}$, so $\forall x \in X$ we have
\begin{align*}
  J'_{31x} \cap H'  
&=((J'_{3x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{1} ) \cap (H\uplus J_1 \setminus\{k\} )\\
&=((J'_{3x}\cap (H\uplus J_1))\uplus (J^{2 \prime}_{1}\cap (H\uplus J_1)))\setminus \mbrc{k}\\
&=((J'_{3x}\cap H)\uplus (J^{2 \prime}_{1}\cap  J_1))\setminus \mbrc{k}\text{ since } J_1\cap J'_{3x} = \emptyset \text{ and } H\cap J^{2 \prime}_{1} = \emptyset\\
& =((J'_{3x}\cap H)\uplus J^{2 \prime}_{1})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{1}\subseteq J_1\\
& =((J'_2\cap H)\uplus J^{1 \prime}_{1})\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
&= ((J'_2 \cap H) \uplus (J^{1 \prime}_{1} \cap J_1)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{1}\subseteq J_1\\ 
& = (J'_2\cap (J_1 \uplus H)) \uplus ((J^{1 \prime}_{1} \cap (J_1 \uplus H)) \setminus \mbrc{k} \text{ since } J_1\cap J'_{2} = \emptyset \text{ and } H\cap J^{1 \prime}_{1} = \emptyset\\
		& = \mpar{(J'_2  \uplus J^{1 \prime}_{1})\setminus \mbrc{k}} \cap \mpar{(J_{1} \uplus H) \setminus \mbrc{k}}\\
		& = J'_{12} \cap H'
\end{align*}

>>>>

In this case the composition gives: \[g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} \text{ and }
g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}\]
As $k \in H$ we have   
$\beta_{1k} = \beta_{2xk}$ then we  deduce:
\[g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}\]
The proof of the rest  is based on the following facts: 
\begin{enumerate}
\item  Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transitions $t_3$ and .   By construction of  $t_{13}$ and $t_{23x}$ we have $\alpha_{13}=
\alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.
\item By composition we have also: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J'_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^{1\prime} \land \beta^1_{3j}= \beta^2_{3j})\]
\item 
Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: \\
${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
The disjunction with the following hypothesis:\\ $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$  will give:
\begin{align*}
 V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash &    \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in    ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
\Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}
\end{align*}
\end{enumerate}

@@

\RAB{ I think there is no need to the no blocking condition} Furthermore, by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
Thus, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13}  \cancel{\wedge \reach{A_{13}}\mpar{s_{13}}}
\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
		  \wedge \cancel{\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
\wedge} \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
		\end{array}}   
\end{multline*}

From the two previous formulas, we get:
\begin{multline*}
V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
R\mpar{s_1, s_{2}} \wedge g_{13} \land \cancel{\reach{A_{13}}\mpar{s_{13}} \land} \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  \cancel{\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}}		\nwedge\\
			  R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
 \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
		\end{array}}   
\end{multline*}

@@

\item \TODO{To check from this point:} Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
\begin{multline*}
V_{13} \uplus V_{23}  \vdash  R\mpar{s_{13}, s_{23}} \nwedge  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg (\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}) 
\end{multline*}

Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
\begin{multline*}
V_1 \uplus V_2 \vdash R\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies   \neg(\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2})
\end{multline*}
Because the guards from transitions of $A_1$ are still transitions of $A_{13}$, we get:  
\begin{multline*}
V_{13}   \vdash \neg(\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
\end{multline*}

Similarly, transitions of $A_2$ are still transitions of $A_{23}$,  we get:
\begin{multline*}
V_{23}   \vdash \neg(\bigvee_\subbox{t_1 \in \fOT{s_2}} \fguard{t_2}) \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
\end{multline*}
From the three previous formulas we deduce:
  \begin{multline*}
V_{13} \uplus V_{23} \vdash R\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
\end{multline*}

which also implies:
\begin{multline*}
V_{13} \uplus V_{23}  \vdash \\ \underbrace{R\mpar{s_1, s_2} \wedge  \mpar{\,\,\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 \wedge s^1_3=s^2_3}}_{R^{\prime}(s_{13},s_{23})}  \wedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})   \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
\end{multline*}
which gives us what we needed to demonstrate. \qed

@@

\begin{align*}
		&  \OTx{12}{}{12}{12} \in \fOT{s_{12}}
\end{align*}		
there exists an indexed family $t_{13x}$ of OTs originating from $s_{13}$ that simulates it: 
\begin{align*}
		&  \mpar{\OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X}
\end{align*}	
such that  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
\begin{multline*}	
V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
		\end{array}} 
	\end{multline*}
By definition of composition and open automata refinement we have: 
\begin{align*}
&V_{12}= V^1_1\uplus V_3 \text{ and }
V_{13}= V^2_1\uplus V_3\\
& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\} = \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} = J_{12 } \cap J_{13} 
\end{align*}
We have by hypothesis $\wrel{A_2}{A_3}{H}$, then for any open transition $t_2$ in $T_2$  originating from $s_2$:
\begin{align*}
\OTx{2}{}{2}{2} \in \fOT{s_2}
\end{align*}
there exists an indexed family of OTs originating from $s_{2}$: 
\begin{align*}
\mpar{\OTx{3}{x}{3x}{3x} \in \fOT{s_{3}}}^{x \in X} 
\end{align*}
such that $\forall x \in X, J'_{3x} \cap H = J'_2 \cap H$ and
\begin{multline*}
%\everymath{\displaystyle}
V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ R\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj} \nwedge\\
			 g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
		\end{array}}  \qquad \quad (*)
\end{multline*}	
\smallskip

@@

\paragraph{First case: Both automata perform a transition.} The transition $t_{12}$  is obtained by the composition of transition $t_2=\OTx{2}{}{2}{2}$ and a transition \[t_1^1=
\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
\] The result:
%%%% Attention deactiver ici
\[
t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}',s'_2 }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2j})^{j \in J^{\prime}_2} }}{g^1_1 \wedge g_2 \wedge \alpha^1_1 = \beta_{2k}}{\psi^1_1 \uplus \psi_2} \qquad \text{ where } k \in {J^1_{1}}^{\prime} 
\]

We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (as stated above).
By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$.
\[
t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{j \in J^{2 \prime}_1}}\uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}} }{g_{3x} \wedge g^2_1 \wedge \alpha^2_1 = \beta_{3xk}}{\psi_{3x} \uplus \psi^2_1}
\right)^{x\in X}\]
Recall that in this case  $k \in {J^1_{1}}^{\prime}$, so $\forall x \in X$ we have:
\begin{align*}
  J'_{31x} \cap H'  
&=((J'_{3x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{1} ) \cap (H\uplus J_1 \setminus\{k\} )\\
&=((J'_{3x}\cap (H\uplus J_1))\uplus (J^{2 \prime}_{1}\cap (H\uplus J_1)))\setminus \mbrc{k}\\
&=((J'_{3x}\cap H)\uplus (J^{2 \prime}_{1}\cap  J_1))\setminus \mbrc{k}\text{ since } J_1\cap J'_{3x} = \emptyset \text{ and } H\cap J^{2 \prime}_{1} = \emptyset\\
& =((J'_{3x}\cap H)\uplus J^{2 \prime}_{1})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{1}\subseteq J_1\\
& =((J'_2\cap H)\uplus J^{1 \prime}_{1})\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
&= ((J'_2 \cap H) \uplus (J^{1 \prime}_{1} \cap J_1)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{1}\subseteq J_1\\ 
& = (J'_2\cap (J_1 \uplus H)) \uplus ((J^{1 \prime}_{1} \cap (J_1 \uplus H)) \setminus \mbrc{k} \text{ since } J_1\cap J'_{2} = \emptyset \text{ and } H\cap J^{1 \prime}_{1} = \emptyset\\
		& = \mpar{(J'_2  \uplus J^{1 \prime}_{1})\setminus \mbrc{k}} \cap \mpar{(J_{1} \uplus H) \setminus \mbrc{k}}\\
		& = J'_{12} \cap H'
\end{align*}

In this case the composition gives: \[g_{12} \Leftrightarrow g^1_1 \wedge g_2 \wedge \alpha^1_1=\beta_{2k} \text{ and }
g_{13x}  \Leftrightarrow g^2_1 \wedge g_{3x} \wedge  \alpha^2_1=\beta_{3xk}\]
As $k \in H$ we have   
$\alpha^1_1= \alpha^2_1$ then we  deduce:
\[g^1_1 \wedge \alpha^1_1=\beta_{2k}  \Leftrightarrow g^2_1 \wedge \alpha^2_1= \beta_{3xk}\]
